Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2015-03-11 paper/poly.tex
add clumsy proof
odd spacing
include graphics

We now define an interpretation $P_.^y$ of indices containing
$\square$:
\begin{align*}
P^y_{(\square,z)}(\state) &=
  \left| [\sigma(x){+}\sigma(y), \sigma(z)] \,\triangle\,
         [\sigma(x), \sigma(z)] \right| \\
P^y_{(z,\square)}(\state) &=
  \left| [\sigma(z), \sigma(x){+}\sigma(y)] \,\triangle\,
         [\sigma(z), \sigma(x)] \right| \\
P^y_{(\square, \square)}(\state) &= 0 \\
P^y_{(u,v)}(\state) &= |[\sigma(u), \sigma(v)]|,
\end{align*}
we use $A \,\triangle\, B$ to denote the symmetric difference
of $A$ and $B$.
The quantity $P^y_{(\square,z)}(\state)$ is the size change of
the interval $[x, z]$.  If $\state$ is the state before the
assignment and $\state'$ is the state after the assignment, we
have
$P_{(x,z)}(\state) = P^y_{(x,z)}(\state') + P^y_{(\square,z)}(\state')$
and
$P_{(z,x)}(\state) = P^y_{(z,x)}(\state') - P^y_{(z,\square)}(\state')$.
With these definitions, we have the following lemma.
\begin{lemma}
If $\state \rightarrow_C \state'$ and $\state(y)>0$ then
$P_Q(\state) = P^y_{\qsh^+_x Q}(\state')$.
\end{lemma}

>>>>

We now define an interpretation $P_.^y$ of indices containing
$\square$:
\begin{align*}
P^y_{(\square,z)}(\state) &=
  \left| [\sigma(x){+}\sigma(y), \sigma(z)] \,\triangle\,
         [\sigma(x), \sigma(z)] \right| \\
P^y_{(z,\square)}(\state) &=
  \left| [\sigma(z), \sigma(x){+}\sigma(y)] \,\triangle\,
         [\sigma(z), \sigma(x)] \right| \\
P^y_{(\square, \square)}(\state) &= P_{(x,\square)}(\state)
  = P_{(\square,x)}(\state) = 0 \\
P^y_{(u,v)}(\state) &= |[\sigma(u), \sigma(v)]|,
\end{align*}
we use $A \,\triangle\, B$ to denote the symmetric difference
of $A$ and $B$.
The quantity $P^y_{(\square,z)}(\state)$ is the size change of
the interval $[x, z]$.  If $\state$ is the state before the
assignment and $\state'$ is the state after the assignment, we
have
$P_{(x,z)}(\state) = P^y_{(x,z)}(\state') + P^y_{(\square,z)}(\state')$
and
$P_{(z,x)}(\state) = P^y_{(z,x)}(\state') - P^y_{(z,\square)}(\state')$.
With these definitions, we have the following lemma.
\begin{lemma}
If $\state \rightarrow_C \state'$ and $\state(y)>0$ then
$P_Q(\state) = P^y_{\qsh^+_x Q}(\state')$.
\end{lemma}
\begin{proof}
\small
\begin{align*}
&P^y_{\qsh_x^+ Q}(\state')
= \sum_I q'_I \prod_{(u,v)} P_{uv}^{uv} \\
&= \sum_I q_{I[\square\gets x]} P_I \prod_z
  \binom{\square z {+} xz}{\square z}P_{\square z}^{\square z} P_{xz}^{xz}
  \binom{z\! \square\! {+} zx}{z \square}(-P_{z \square})^{z \square} P_{zx}^{zx} \\
&= \sum_J q_J P_J \sum_{I[\square\gets x] = J} \prod_z
  \binom{\square z {+} xz}{\square z}P_{\square z}^{\square z} P_{xz}^{xz}
  \binom{z\! \square\! {+} zx}{z \square}(-P_{z \square})^{z \square} P_{zx}^{zx} \\
&= \sum_J q_J P_J \prod_z
  \left( \sum_{\square z + xz = j_{xz}}
    \binom{\square z {+} xz}{\square z}P_{\square z}^{\square z} P_{xz}^{xz} \right)
  \left( \sum_{z\square {+} zx = j_{zx}} \dots \right) \\
&= \sum_J q_J P_J \prod_z
  (P_{xz} + P_{\square z})^{j_{xz}}
  (P_{zx} - P_{z \square})^{j_{zx}} \\
&= \sum_J q_J P_J(\state) = P_Q(\state)
\end{align*}
\end{proof}

\paragraph{Projection of Resource Polynomials}

\DeclareGraphicsRule{*}{mps}{*}{}

The shift operation perserves all the potential after an increment
but it introduces a new dummy variable $\square$.  Because annotations
need to be uniform for compositionality, we present in this paragraph
a projection that eliminates this extra variable.  The main identity that
we use is $P_{\square z}(\state) + P_{z \square}(\state) =
P_{0y}(\state)$.  It can be checked on all the three cases illustrated
below.
$$
\includegraphics{fig/ivals.1}
$$
In the first case, $P_{\square z}$ will be 0 and $P_{z \square}$ will
be non zero; the third case witnesses the opposite situation; and in
the second case, both are non-zero.
